\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-29 syntactic-example.tex
syntactical → syntactic
Reply the comments.

Now we construct the recursor, with the help of the handler module
$"handler"_1$, with which we can construct the real recursor $"pred"_1$.
Both detailed constructions are omitted. Then we again abstract the
concrete recursor $"pred"_1$ away using $"sl"_4$ so that the field $"k"$
can apply it without resorting to the concrete recursor. Finally we
have $"sig"_5$ as final signature.\YZ{
  Maybe it is a good place to point out what El(pjr (pjl pi_2)) in pN_2 stands for
  and what El(W(pjr(pjl^2 pi_2))) in predT stands for.
}

>>>>

Now we construct the recursor, with the help of the handler module
$"handler"_1$, with which we can construct the real recursor $"pred"_1$.
Both detailed constructions are omitted. Then we again abstract the
concrete recursor $"pred"_1$ away using $"sl"_4$ so that the field $"k"$
can apply it without resorting to the concrete recursor. Finally we
have $"sig"_5$ as final signature. Recall from \ruleref{Sigma Elim}, we have "pjl" and "pjr" as two projection from the sigma type (dependent pair). We will also use $"pjl"^n$ as a consecutive composition of "pjl", (e.g. $"pjl"^2~t$ is exactly $("pjl" ("pjl"~t))$ ). \YZ{
  Maybe it is a good place to point out what El(pjr (pjl pi_2)) in pN_2 stands for
  and what El(W(pjr(pjl^2 pi_2))) in predT stands for.
}\EDJreply{Done.}
